\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/applications.tex
refining applications (with limitation for complex devices) and commented 'comments' in disucssion

\ben{We may need to add some discussion of applications}.

@@

\sean{here are some parts I can think of to add to this section, feel free to refine/elaborate/remove.}

\changes{During our study, we learned a few things. (1)Our soulution works best on simple applications such as on/off or volume up/down controls. For more complicated controls, we suggest to use a hybrid solution in which HOBS completes the target selection process and seamlessly transfer information to user's smartphone and triggers corresponding app.  (2)Our solution excels at tasks where the user needs to focus primarily on the objects and the information provided by the near-eye display is only supportive, for example, museums or automobile body shops. (3)Our soulution also works well for roles whose hands are constantly occupied from using handheld devices, e.g. chefs.}
%% I feel like we should mention a bit about the interaction complexity. But that's a bit out of the scope of this paper.
%% Participants rated the ease of control of particular appliances differently. Ease of use ratings were higher for the lamp and fan which had simple, discrete on/off actions, and lower for the more complex movie player (see Figure~\ref{fig:smarthome-likert}). Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{Most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. The screen size and (largely) 1D input put a limit on the complexity of interfaces that can be presented. As one participant remarked: \studyquote{[The media player] does not seem to be more efficient than a tablet device.} The difficulty can also partly be ascribed to our interaction design, which required one finger swipes to switch between parameters and two finger gestures for adjusting parameters --- it was hard for users to exert fine control over two-finger swipes. In addition, users did not always remember these mappings as they are not yet part of a standard gesture vocabulary.

%\subsection{Attention Tracking}
%\label{sec:attention-tracking}

%The second tier of applications enabled by our system is an implicit use of users' head orientation. One sample application is to obtain a personal statistics. Nowadays, we are surrounded by all sorts of screens, and many people's job requires them to stare at the monitors for the whole day. 
% citation needed, take a look at this one: E-Readers and Visual Fatigue, http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3873942/
%Knowing how much time you have spent in front of the screen is definitely useful, and the application can be built to remind the user to take a break whenever a certain time threshold is reached.

%% We might be lacking evidence, but let me just write down the draft first.
%Our system enables a flexible and easy-to-use tracking of users' attention without knowing the map. Therefore, it's suitable to be deployed in large museums (even when the exihibits positions are adjusted constantly). Then such attention tracking will facillitate many social science studies. Previous solutions are either using RFID \cite{Hsi:2005:REV:1081992.1082021} or video taping % this is a cv of Adam who has worked on video analysis http://www.exploratorium.edu/vre/cvs/ak_cv.pdf. 
%However, head orientation is a better approximation of attention rather than proximity. By placing our tracking devices in the environment, we can easily get a more accurate profiling of users intention.

%\subsection{Indoor Positioning}
%\label{sec:indoor-positioning}

%There is one category of indoor positioning which is based on angle of arrival. Traditional approaches on indoor positioning are based on fingerprinting or triangulation, which is known to be bad due to multi-path effect for indoor environment. With our system, using the adjacent mapping calibration we can figure out the position of the targets in a room, and then based on a new sample, we can estimate a user's position with some simple math.

>>>>

@@

% \bjoern{1 is problematic - because it sounds like that the head worn device is in the end not worth it and you should just use your phone, even if it takes longer. I'm not sure we can confidently say something about museums or body shops - this sounds speculative. Needs section needs to be rephrased., e.g. as in: Our solution succeeds at X because of Y. This suggests that future applications in domains like Z could be especially promising.}

\changes{Though our solution successfully solves the problem of {\em targets selection}, we haven't addressed the controlling issue when the device becomes complex. Users reported that \studyquote{for more complex appliances (TV), interaction was more difficult}. This problem can be partially ascribed to the limitations of Glass -- the touchpad can only detect a few gestures and the screen is too small. A separate work on interaction techniques for head-worn computing devices is needed to address these issues, while we keep our focus on the target selection in this paper.}

%% I feel like we should mention a bit about the interaction complexity. But that's a bit out of the scope of this paper.
%% Participants rated the ease of control of particular appliances differently. Ease of use ratings were higher for the lamp and fan which had simple, discrete on/off actions, and lower for the more complex movie player (see Figure~\ref{fig:smarthome-likert}). Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{Most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. The screen size and (largely) 1D input put a limit on the complexity of interfaces that can be presented. As one participant remarked: \studyquote{[The media player] does not seem to be more efficient than a tablet device.} The difficulty can also partly be ascribed to our interaction design, which required one finger swipes to switch between parameters and two finger gestures for adjusting parameters --- it was hard for users to exert fine control over two-finger swipes. In addition, users did not always remember these mappings as they are not yet part of a standard gesture vocabulary.
